\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage[colorlinks=true,
            linkcolor=black,
            urlcolor=blue,
            citecolor=black]{hyperref}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{amsmath}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\onehalfspacing

\title{\textbf{Assignment 2: Lean Startup}\\
       \large SendIt -- Peer-to-Peer Secure File Transfer\\[0.5em]
       \normalsize 2DV614}
\author{Emil Ulvagården, Jesper Wingren \& Samuel Berg}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\tableofcontents

\newpage
\section{Choice of Company Form}
The company form decided upon for \textit{SendIt} is a limited company (\textit{Aktiebolag / AB}). This corporate structure was selected over a sole trader (\textit{Enskild firma}) or a partnership for several critical reasons:

\begin{itemize}
    \item \textbf{Liability Mitigation:} Tech startups inherently carry operational and financial risks. In a limited company, the liability is strictly placed on the corporate entity rather than the owners' personal assets, protecting the founders' individual finances.
    \item \textbf{Credibility with Stakeholders:} A limited company establishes immediate professional credibility with banks, institutional investors, and enterprise clients, as the owners must commit a minimum share capital to incorporate.
    \item \textbf{Scalability and Equity Distribution:} The limited company structure allows ownership to be split into shares. This makes it highly scalable, facilitating future venture capital equity financing and the potential implementation of employee stock option programs.
\end{itemize}

\section{Joining an Incubator}
To join a business incubator in the Kronoberg and Växjö region (such as \textit{Företagsfabriken}), a startup must fulfill specific requirements during the screening phase.

{\large \textbf{Key Prerequisites:}}
\begin{itemize}
    \item \textbf{Innovation:} The business concept must possess a unique value proposition or a novel approach to solving a market problem. For \textit{SendIt}, this is achieved through our proprietary peer-to-peer secure transfer protocols.
    \item \textbf{Scalability:} The business model must show high growth potential, meaning revenues can grow exponentially while expenses grow linearly, allowing the company to expand internationally.
    \item \textbf{Dedicated Team:} The incubator requires a committed, driven, and coachable founding team with complementary skill sets—satisfied by our group's unified computer science background.
    \item \textbf{Sustainability:} The idea must align with modern sustainability goals and ethical business practices, ensuring long-term viable operations.
\end{itemize}

\textbf{The Process:} The process typically initiates with a ``Growth Meeting'' (\textit{Tillväxtmöte}) where the founders pitch their initial business canvas. This is followed by an evaluation phase where the core business case and market validity are scrutinized by an admissions jury. Once accepted into the incubator program, the startup gains structured business coaching, tailored growth networks, office space, and direct channels to local investor networks.

\section{Summary of Registration Process}
Based on Bolagsverket guidelines for incorporating an \textit{Aktiebolag}, the registration process involves four main milestones:
\begin{enumerate}
    \item \textbf{Drafting Founding Documents:} Writing the Articles of Association (\textit{Bolagsordning}) and the Memorandum of Association (\textit{Stiftelseurkund}).
    \item \textbf{Capital Deposit:} Opening a corporate bank account, depositing the minimum required share capital, and obtaining an official bank certificate (\textit{Bankintyg}).
    \item \textbf{Form Submission:} Filling out and submitting Form 816 (\textit{Nyregistrering}) to Bolagsverket, or utilizing the digital integration platform on \textit{verksamt.se}.
    \item \textbf{Fee Settlement:} Paying the administrative registration fee to finalize processing, after which the company receives its corporate identity number (\textit{Organisationsnummer}).
\end{enumerate}

\end{document}